### 2019-12-28 docs/thesis-project/article.tex
Update article.tex

\section{Cloud-Assisted P2P Networks}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BEGIN SOLUTION PROPOSAL %
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Solution Proposal}\label{sec:proposal}
%%%%%%%%%%%%%%%%%%%%%%%%%
% END SOLUTION PROPOSAL %
%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BEGIN EVALUATION METHODOLOGY %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Evaluation Methodology}\label{sec:methodology}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
% END EVALUATION METHODOLOGY %
%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\section{Cloud-Assisted P2P Networks}\label{sec:ca-networks}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BEGIN SOLUTION PROPOSAL %
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage\section{Solution Proposal}\label{sec:proposal}
In this section, we introduce a prototype architecture that targets the use case that inspired to explore the theme of this thesis. We explain it by decomposition.

\subsection{Use Case}
Fundamentally, the idea is that a company, Hives, with dedicated web servers called Hiveminds, provides a platform for registered users to sell storage belonging to their personal computers directly to other registered users. Clients pay a monthly fee directly to Hives based on how much storage space they need. Hiveminds then put together a set of sellers, which constitute a Hive, that serves adequate storage space to the clients. Sellers are selected according to the reputation they earn over time based on their reliability, with a bias towards more reputable sellers. The collected fee is distributed proportionately among Hive members according to their overall space contribution and up time, calculated weekly, for example. The company's revenue comes from keeping a small percentage of the monthly fees. If the client requires continuous availability, rather than durability, he may pay a premium, in which case, inspired on the related work mentioned in section \ref{sec:ca-networks}, cloud storage may be used to help the Hive in meeting the required service guarantees. Hive revenue shares are reduced if their reliability degrades too much.

\subsection{Key notes and Assumptions}
\begin{itemize}
    \item Session handling and payment models are out of the scope of this proposal.
    \item Reputation is static, i.e., they are simulation parameters.\footnote{See goals in Section \ref{sec:intro}}
    \item Message integrity and confidentiality are not at risk.
    \item Sellers are not malicious, e.g., do not perform DoS on other sellers.
    \item Sellers may fail without warning, and some absences may be transient.
    \item Cloud service is abstract, i.e., ranges from local to a cloud storage server.
    \item The storage space purpose is backups, thus write operations are rare.\footnote{Write operations possibly cause old versions to be overwritten}
    \item The storage space is not shared, i.e., there are no concurrent writes.
\end{itemize}

\subsection{Hiveminds - Master Servers}

%%%%%%%%%%%%%%%%%%%%%%%%%
% END SOLUTION PROPOSAL %
%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BEGIN EVALUATION METHODOLOGY %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage\section{Evaluation Methodology}\label{sec:methodology}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
% END EVALUATION METHODOLOGY %
%%%%%%%%%%%%%%%%%%%%%%%%%%%
